\begin{longtable}[]{|p{1cm}p{10cm}p{2cm}|}
    \caption{Questions defined during the instantiation of EFFORT.}
    \label{table:questions_minified}\\
    \toprule
Id & Question & Relevance \\
\midrule
\endhead
1a.1 & What degree of Adaptability does the product offer?$^{\square}$ & 2 \\
1a.2 & What degree of Installability does the product offer?$^{\square}$ & 1 \\
1a.3 & What degree of Replaceability does the product offer?$^{\square}$ & 2 \\
1a.4 & What degree of Coexistence does the product offer?$^{\times}$ & \\
1b.1 & What degree of Analyzability does the product offer?$^{\square}$ & 2 \\
1b.2 & What degree of Changeability does the product offer?$^{\times}$ & \\
1b.3 & What degree of Testability does the product offer?$^{\square}$ & 2 \\
1b.4 & What degree of Technology concentration does the product offer?$^{\times}$ & \\
1b.5 & What degree of Stability does the product offer?$^{\square}$ & 2 \\
1b.6 & How maintainable is the application code using the product?* & 2 \\
1c.1 & What degree of Rebustness does the product offer?$^{\times}$ & \\
1c.2 & What degree of Recoverability does the product offer?$^{\times}$ & \\
1d.1 & What degree of Functional adequacy does the product offer?$^{\square}$ & 3 \\
1d.2 & What degree of Interoperability does the product offer?$^{\square}$ & 2 \\
1d.3 & What degree of Functional accuracy does the product offer?$^{\square}$ & 2 \\
1e.1 & What degree of Pleasantness does the product offer?$^{\times}$ & \\
1e.2 & What degree of Operability does the product offer?$^{\square}$ & 1 \\
1e.3 & What degree of Understandability does the product offer?$^{\times}$ & \\
1e.4 & What degree of Learnability does the product offer?$^{\square}$ & 2 \\
1f.1 & What degree of Time behavior does the product offer?$^{\square}$ & 2 \\
1f.2 & What degree of Resources utilization does the product offer?$^{\square}$ & 3 \\
2.1 & How many developers does the community involve?$^{\square}$ & 3 \\
2.2 & What degree of activity does the community have?$^{\square}$ & 2 \\
2.3 & Are the support tools available and effective?$^{\square}$ & 2 \\
2.4 & Are support services provided?$^{\square}$ & 1 \\
2.5 & Is the documentation exhaustive and easily consultable?$^{\square}$ & 3 \\
3.1 & What degree of functional adequacy does the product offer?$^{\square}$ & 3 \\
3.2 & What degree of diffusion does the product achieve?$^{\square}$ & 2 \\
3.3 & What level of cost-effectiveness is estimated?$^{\times}$ & \\
3.4 & What degree of reusability and redistribution is left by the
license?$^{\square}$ & 1 \\
\bottomrule
\end{longtable}
